My title

### 2024-03-16 paper/paper.qmd
Save RDS to the file of models

library(tidyverse)
library(palmerpenguins)
library(boot)
library(broom.mixed)
library(collapse)
library(dataverse)
library(gutenbergr)
library(janitor)
library(knitr)
library(marginaleffects)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(tidyverse)
```

@@

political_preferences <-
  stan_glm(
    voted_for ~ gender + education,
    data = ces2022_reduced,
    family = binomial(link = "logit"),
    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
    prior_intercept = 
      normal(location = 0, scale = 2.5, autoscale = TRUE),
    seed = 853
  )

saveRDS(
  political_preferences,
  file = "political_preferences.rds"
)
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
political_preferences <-
  readRDS(file = "political_preferences.rds")
```

>>>>

library(tidyverse)
library(palmerpenguins)
library(boot)
library(broom.mixed)
library(collapse)
library(dataverse)
library(gutenbergr)
library(janitor)
library(knitr)
library(marginaleffects)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(tidyverse)
library(arrow)
```

@@

political_preferences <-
  stan_glm(
    voted_for ~ gender + education,
    data = ces2022_reduced,
    family = binomial(link = "logit"),
    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
    prior_intercept = 
      normal(location = 0, scale = 2.5, autoscale = TRUE),
    seed = 812
  )

saveRDS(
  political_preferences,
  file = "models/political_preference.rds"
)
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
political_preferences <-
  readRDS(file = "models/political_preferences.rds")
```
